The expected shape of the Milky Way's Dark Matter halo

### 2018-09-18 Paper/paper.tex
edit paper

%This is a simple template for authors to write new MNRAS papers.
%See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
%for a full user guide.

\citep{2011MNRAS.416.1377V}

@@

One of the principal predictions of the CDM model is that DM halos are ellipsoidal and very well characterized by the principal axes $a>b>c$. This is due, among other causes, to the anisotropical and clumpy accretion of matter influenced by environmental structures \citep[see?][]{Colberg et al. 1999, Vera-Ciro et al. 2011}. The general concensus in numerical simulations \citep[e.g.][]{Dubinski and Calberg 1991,Hayashi et al. 2007} is that halos tend to be prolate with axial ratios $\left(b/a\right)_{\rho}$ ~ \textit{number}, $\left(c/a\right)_{\rho}$ ~ \textit{number} and small differences may arise by the use different methods in numerical recipies for the simulations and the shape-calculation methods  \citep[see][]{Allgood et al. 2006}. Some studies have gone a step further as for analyzing the dependence of shape of the DM halo on the radius and redshift \citep[e.g.][]{Allgood et al. 2006,Vera-Ciro et al. 2011}, generally finding that halos are rounder at the outerskirts and at lower redshift.\\

@@

In the case of the Milky Way, where we have a three-dimensional view from the inside, there seems to be a general agreement for oblate (i.e. a=b>c) configurations at small distances around \~ <20kpc \citep[see][]{Law_and_Majewski_2010,Bovy2016,Loebman,Vera-Ciro, RobOllingMerrifield,Bovy,BanerjeeChanda}, and more triaxial and prolate configurations on the outter distances \~>20kpc \citep[see][]{Vera-Ciro,Law_and_Majewski_2009,Deg,BanerjeeChanda}. However, some studies are inclined towards prolate configurations even at the inner parts of the halo \citep[see][]{BowdenEvansWilliams,Findothers}, and although it previously seemed that a triaxial DM halo on the outerskirts would be necessary to fully explain the characterization of the Sagittarius stream \citep[see][]{Law_and_Majewski_2009}, more recent studies put into doubt (question) this claim by reporting inconsistencies with narrow stellar streams \citet{PearsonKupperJohtnston, MoreLikeThis} or finding that the relaxation of other constraints may make this claim unnecessary (wording) \citet{IbataLewisMartin}.\\

Although observations predict more symmetric halos than DM-only simulations, there is strong evidence claiming that the presence of baryons need/make more axisymmetrical halos. Some studies have shown that to ensure the stability of a hydrodynamical (numeric) disk artificially embeded in a static(non-changing) DM halo, its shape must be axisymmetrical \cite{}. Other works have studied this rounding effect by emulating a disk as an adiabatically growing potential inside an N-body triaxial DM halo \cite{Debattista_et_al._2008,Debattista-Roskar, katzantzidis}, finding that (findings of this study -debattista-). Other works of this type?\\

>>>>

A robust prediction of the Cold Dark Matter (CDM) model is that DM
halos are ellipsoidal and can be characterized by the principal axes
$a>b>c$.  
The ellipsoidal shape is mostly due to the anisotropical and
clumpy accretion of matter influenced by environmental structures.

The general concensus in numerical simulations is that halos tend to
be prolate with axial ratios b/a ~ \textit{number}, $c/a$
~ \textit{number} and small differences may arise by the use different
methods in numerical recipies for the simulations and the
shape-calculation methods  \citep{Allgood_et_al._2006}. Some
studies have gone a step further as for analyzing the dependence of
shape of the DM halo on the radius and redshift
\citep[e.g.][]{Allgood_et_al._2006}, generally
finding that halos are rounder at the outerskirts and at lower
redshift.

\citep{Vera-Ciro_et_al._2011}

@@

@@

In the case of the Milky Way, where we have a three-dimensional view from the inside, there seems to be a general agreement for oblate (i.e. a=b>c) configurations at small distances around \~ <20kpc \citep[see][]{LM10,Bovy2016,Loebman,Vera-Ciro, RobOllingMerrifield,Bovy,BanerjeeChanda}, and more triaxial and prolate configurations on the outter distances \~>20kpc \citep[see][]{Vera-Ciro,LMJ09,Deg,BanerjeeChanda}. However, some studies are inclined towards prolate configurations even at the inner parts of the halo \citep[see][]{BowdenEvansWilliams,Findothers}, and although it previously seemed that a triaxial DM halo on the outerskirts would be necessary to fully explain the characterization of the Sagittarius stream \citep[see][]{LMJ09}, more recent studies put into doubt (question) this claim by reporting inconsistencies with narrow stellar streams \citet{PearsonKupperJohtnston, MoreLikeThis} or finding that the relaxation of other constraints may make this claim unnecessary (wording) \citet{IbataLewisMartin}.\\

Although observations predict more symmetric halos than DM-only simulations, there is strong evidence claiming that the presence of baryons need/make more axisymmetrical halos. Some studies have shown that to ensure the stability of a hydrodynamical (numeric) disk artificially embeded in a static(non-changing) DM halo, its shape must be axisymmetrical \cite{}. Other works have studied this rounding effect by emulating a disk as an adiabatically growing potential inside an N-body triaxial DM halo \cite{Debattista-Moore,Debattista-Roskar, katzantzidis}, finding that (findings of this study -debattista-). Other works of this type?\\
